\pdftitle

### 2017-05-18 maxNt.tex
added some references

Recent electrophysiological techniques \cite{***} in fact allow
experimenters to record samples of even a couple hundreds neurons from
specific brain areas. These samples are usually picked out according to an
unknown process, but from their observation we expect to learn something
about all other neurons in the same brain area. That is, we assumed
that they are a \enquote{representative random sample}.

@@

These computational costs are one, probably not the earliest, of the many
reasons why \me\ methods have been introduced in neuroscience. It would be
useful to somehow compress the statistical wealth of large neuronal
recordings into few quantities, like sample moments for example. This
compression would also entail interesting physico-biological properties of
neuronal activity. The standard \me\ method
\cite{jaynes1957,sivia1996_r2006,meadetal1984} accomplishes this kind of
compression: it associates a unique probability distribution with few
experimental quantities \cite{***}. But this is only one of its uses. It is
also used for various information-theoretic purposes or to generate
reference probability distributions \cite{***}. In all these uses the \me\
distribution is chosen as the \enquote{maximally noncommittal} one
\cite{jaynes1963}. This adjective means little without further technical
characterizations. Different works give different characterizations, but in
this paper we will use the quoted expression as an umbrella term for all of
them. Our results will not depend on the specific characterization of
\enquote{noncommittal}.

>>>>

Recent electrophysiological techniques \cite{berenyietal2014} in fact allow
experimenters to record samples of even a couple hundreds neurons from
specific brain areas. These samples are usually picked out according to an
unknown process, but from their observation we expect to learn something
about all other neurons in the same brain area. That is, we assumed
that they are a \enquote{representative random sample}.

@@

These computational costs are one, probably not the earliest, of the many
reasons why \me\ methods have been introduced in neuroscience. It would be
useful to somehow compress the statistical wealth of large neuronal
recordings into few quantities, like sample moments for example. This
compression would also entail interesting physico-biological properties of
neuronal activity. The standard \me\ method
\cite{jaynes1957,sivia1996_r2006,meadetal1984} accomplishes this kind of
compression: it associates a unique probability distribution with few
experimental quantities \cite{***}.
But this is only one of its uses. It is
also used for various information-theoretic purposes or to generate
reference probability distributions \cite{schneidmanetal2006,shlensetal2006,roudietal2009b,tkaciketal2014b}.
In all these uses the \me\
distribution is chosen as the \enquote{maximally noncommittal} one
\cite{jaynes1963}. This adjective means little without further technical
characterizations. Different works give different characterizations, but in
this paper we will use the quoted expression as an umbrella term for all of
them. Our results will not depend on the specific characterization of
\enquote{noncommittal}.
